Community engagement and subgroup meta-knowledge: Some factors in the soul of a community

### 2015-08-05 PaperFinalDraft.Rnw
using is.na() instead of quoted NA. Closes #6

<<missingdatatable, results="asis">>=
missing10 <- group_by(sotc10, recommend == "NA") %>% summarise(n = n()) 
missing09 <- group_by(sotc09, recommend == "NA") %>% summarise(n = n()) 
missing08 <- group_by(sotc08, recommend == "(Refused)") %>% summarise(n = n()) 
missing <- c(missing08$n[2], missing09$n[2], missing10$n[2])
missingtable <- as.matrix(data.frame(Year=c(2008, 2009, 2010), Missing=missing, Total=c(dim(sotc08)[1], dim(sotc09)[1], dim(sotc10)[1]), Percent=missing/c(dim(sotc08)[1], dim(sotc09)[1], dim(sotc10)[1])*100))
rownames(missingtable) <- NULL
print(xtable(x=missingtable,caption="Percent of missing data from surveys. The 2010 survey has almost 25 percent missing data. The total number of entries in 2010 is also much larger, suggesting that the 2008 and 2009 datasets used a different criteria for inclusion of entries.", display=c("d", "d", "d","d", "f"), label="missingtable"),include.rownames=FALSE)
@

@@

<<OverallSeniors>>=
seniorGroup10 <- filter(sotc10, seniors != "NA") %>% group_by(citystate, age >= 62, seniors) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2010)

@@

seniorGroup09 <- filter(sotc09, age != "NA") %>% group_by(citystate, age >= 62, seniors) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2009)
names(seniorGroup09) <- n1

@@

<<kidsbyYear>>=
kidGroup10 <- filter(sotc10, children == "Yes" | children == "No", families_kids != "NA") %>% group_by(citystate, children, families_kids) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2010)
names(kidGroup10) <- n1

kidGroup09 <- filter(sotc09, children == "Yes" | children == "No", families_kids != "NA") %>% group_by(citystate, children, families_kids) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2009)
names(kidGroup09) <- n1

@@

kidGroup08 <- filter(sotc08, children == "Yes" | children == "No", families_kids != "NA" & families_kids != "(DK)" & families_kids != "(Refused)") %>% group_by(citystate, children, families_kids) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2008)
names(kidGroup08) <- n1

>>>>

<<missingdatatable, results="asis">>=
count_na <- function(x) sum(is.na(x))
missing10 <- count_na(sotc10$recommend)
missing09 <- count_na(sotc09$recommend)
missing08 <- count_na(sotc08$recommend)
missing <- c(missing08, missing09, missing10)
missingtable <- as.matrix(data.frame(Year=c(2008, 2009, 2010), Missing=missing, Total=c(dim(sotc08)[1], dim(sotc09)[1], dim(sotc10)[1]), Percent=missing/c(dim(sotc08)[1], dim(sotc09)[1], dim(sotc10)[1])*100))
rownames(missingtable) <- NULL
print(xtable(x=missingtable,caption="Percent of missing data from surveys. The 2010 survey has almost 25 percent missing data. The total number of entries in 2010 is also much larger, suggesting that the 2008 and 2009 datasets used a different criteria for inclusion of entries.", display=c("d", "d", "d","d", "f"), label="missingtable"),include.rownames=FALSE)
@

@@

<<OverallSeniors>>=
seniorGroup10 <- filter(sotc10, is.na(seniors) == FALSE) %>% group_by(citystate, age >= 62, seniors) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2010)

@@

seniorGroup09 <- filter(sotc09, is.na(age) == FALSE) %>% group_by(citystate, age >= 62, seniors) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2009)
names(seniorGroup09) <- n1

@@

<<kidsbyYear>>=
kidGroup10 <- filter(sotc10, children == "Yes" | children == "No", is.na(families_kids) == FALSE) %>% group_by(citystate, children, families_kids) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2010)
names(kidGroup10) <- n1

kidGroup09 <- filter(sotc09, children == "Yes" | children == "No", is.na(families_kids) == FALSE) %>% group_by(citystate, children, families_kids) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2009)
names(kidGroup09) <- n1

@@

kidGroup08 <- filter(sotc08, children == "Yes" | children == "No", is.na(families_kids) == FALSE & families_kids != "(DK)" & families_kids != "(Refused)") %>% group_by(citystate, children, families_kids) %>% summarise(n = n()) %>% mutate(frac=prop.table(n), year=2008)
names(kidGroup08) <- n1
